---
title: "Cropdatape: Open Data of Agricultural Production of Crops of Peru"
author: "Agroinformatic Group"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Open data in agriculture is becoming crucial in order to give unrestricve access and reproducible sets of data worldwide. Large amounts of data regarding to yields, harvest areas, food production and nutrition, among others; are relevant to quantify how much we need to feed a big population that is increasing every year. However, this information is stored in formats and files that are not easy to retrieve and analyze. Reseachers, students, and people in general, spend huge amount time and effort cleaning data to get it ready for analysis `(Tidy Data, Hadley W, 2014)`.

Peru is one the most important countries in term of bioversity and food production around the wolrd. Nevertheless, the access to open, clean and curated data is critical. For this reason, `cropdata` arises as an initiave to provide open and cleaned data ready to use. This package have been developed by researchers and students interested in promote findability and accessibility of agricultural crop's production in Peru using `R` and `tidy principles`.


`cropdatape` provides peruvian agricultural production data from the Agriculture Minestry of Peru (MINAGRI). The first version includes `6` crops: `rice`, `quinoa`, `potato`, `sweet potato`, `tomato` and `wheat`; all of them across `24` departments. Initially,  in excel files which has been transformed and assembled using tidy data principles, i.e. each variable is in a column, each observation is a row and each value is in a cell. The variables variables are `sowing` and `harvest area per crop`, `yield`, `production` and `price per plot`, every one year, from `2004` to `2014`.

#Usage

First of all, you can install `cropdatape` directly from CRAN:
```{r, echo=FALSE, message = FALSE}
library("cropdatape")
```



<!-- Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format: -->

<!-- - Never uses retina figures -->
<!-- - Has a smaller default figure size -->
<!-- - Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style -->

<!-- ## Vignette Info -->

<!-- Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette. -->

<!-- ## Styles -->

<!-- The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows: -->

<!--     output:  -->
<!--       rmarkdown::html_vignette: -->
<!--         css: mystyles.css -->

<!-- ## Figures -->

<!-- The figure sizes have been customised so that you can easily put two images side-by-side.  -->

<!-- ```{r, fig.show='hold'} -->
<!-- plot(1:10) -->
<!-- plot(10:1) -->
<!-- ``` -->

<!-- You can enable figure captions by `fig_caption: yes` in YAML: -->

<!--     output: -->
<!--       rmarkdown::html_vignette: -->
<!--         fig_caption: yes -->

<!-- Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**. -->

<!-- ## More Examples -->

<!-- You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`. -->

<!-- ```{r, echo=FALSE, results='asis'} -->
<!-- knitr::kable(head(mtcars, 10)) -->
<!-- ``` -->

<!-- Also a quote using `>`: -->

<!-- > "He who gives up [code] safety for [code] speed deserves neither." -->
<!-- ([via](https://twitter.com/hadleywickham/status/504368538874703872)) -->
